Dependent Object Types

### 2012-08-30 doc/candidacy/macros.tex
ex
basic example for tribe

\lstset{
  literate=
  {=>}{$\Rightarrow\;$}{2}
  {<:}{$<:\;$}{1}
}

@@

% \lstset{basicstyle=\footnotesize\ttfamily, breaklines=true, language=scala, tabsize=2, columns=fixed, mathescape=false,includerangemarker=false}
% thank you, Burak 
% (lstset tweaking stolen from
% http://lampsvn.epfl.ch/svn-repos/scala/scala/branches/typestate/docs/tstate-report/datasway.tex)
\lstset{
    xleftmargin=2em,%
    framesep=5pt,%
    frame=none,%
    captionpos=b,%
    fontadjust=true,%
    columns=[c]fixed,%
    keepspaces=false,%
    basewidth={0.56em, 0.52em},%
    tabsize=2,%
    basicstyle=\small\tt,% \small\tt
    commentstyle=\textit,%
    keywordstyle=\bfseries,%
    escapechar=\%,%
}

>>>>

\lstset{
  literate=
  {=>}{$\Rightarrow\;$}{2}
  {<:}{$<:\;$}{1}
  {<-}{$\leftarrow\;$}{2}
}

@@

% \lstset{basicstyle=\footnotesize\ttfamily, breaklines=true, language=scala, tabsize=2, columns=fixed, mathescape=false,includerangemarker=false}
% thank you, Burak 
% (lstset tweaking stolen from
% http://lampsvn.epfl.ch/svn-repos/scala/scala/branches/typestate/docs/tstate-report/datasway.tex)
\lstset{
    xleftmargin=1em,%
    framesep=5pt,%
    frame=none,%
    captionpos=b,%
    fontadjust=true,%
    columns=[c]fixed,%
    keepspaces=false,%
    basewidth={0.56em, 0.52em},%
    tabsize=2,%
    basicstyle=\footnotesize\tt,% \small\tt
    commentstyle=\textit,%
    keywordstyle=\bfseries,%
    escapechar=\%,%
}

### 2012-08-30 doc/candidacy/report.tex
added TODOs for examples
basic example for tribe

@@

@@

>>>>

% TODO: example of translucent module and its utility. woudl be nice to re-use this example in nuObj to show how it can be encoded

@@

Let's now re-use an example from the paper, and discuss how we would
emulate it in Scala.
\begin{lstlisting}
class Graph {
  class Node {
    Edge connect(Node other) {
      return new Edge(this, other);
    }
  }
  class Edge {
    Node from, to;
    Edge(Node f, Node t) { from = f; to = t; }
  }
}

class ColouredGraph extends Graph { // subclassing
  class Node {                      // further binding
    Colour nodeColour;
  }
}

class Library {
  int distance(Graph.Node n1, n1.out.Node n2) { ... }

  e.out.Edge copyEdge(Graph.Edge e) {
    e.out.Node from = e.from;
    e.out.Node to = e.to;
    new e.out.Edge(from, to);
  }
}
\end{lstlisting}

The ``tests'' are:
\begin{lstlisting}
final ColouredGraph cg1, cg2;
cg1.Node cn1, cn3;
cg2.Node cn2;
cn1.connect(cn3); // Type Correct
cn2.connect(cn3); // Type Error!!!
\end{lstlisting}

Now, we can emulate this Tribe example in Scala at the expense of some
synctactic overhead, since further binding and ``out'' selection are
not native.
\lstinputlisting{tribe.scala}

@@

% TODO: example of module encoding... perhaps in Scala rather than nuObj?
